HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-10-07 paper/main.tex
Fixed typo, added final camera ready to git
switch to emnlp style
Removed eg. still a paragraph over page limit

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
%\usepackage{hyperref}
\usetikzlibrary{positioning}

\aclfinalcopy

@@

\begin{figure*}[t]
\begin{tikzpicture}
\node(tree) [] {\includegraphics[width=1\textwidth]{tree_653_de1_de2.pdf}};
\node [below right = -2cm and  -8cm of tree]{\includegraphics[width=0.4\textwidth]{DAline-extract.png}};
\end{tikzpicture}
%\begin{tabular}{c}
%\includegraphics[width=1\textwidth]{tree_653_ver2.png}\\
%\includegraphics[width=0.6\textwidth]{DAline-extract.png}
%\end{tabular}
\caption{An example of a doubly annotated HUME en-de sentence. The color of the nodes correspond to their
  HUME label: yellow (A), blue (B), and atomic nodes with their traffic. Nodes in which the annotators
  disagree are split in color. The scale at the bottom right shows a sample of 10 raw DA assessments
  for this example. }
\label{fig:humeeg}
\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

%While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
%differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence.
The figure illustrates the conceptual difference between the measures:
while DA standardises and averages scores across annotators to denoise the
crowd-sourced raw data, thus obtaining a single aggregate score,
HUME decomposes over a combinatorial structure, thus allowing to
localize the translation errors. We now turn to comparing HUME to a more
conceptually-related  measure, namely HMEANT.

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
%\usepackage{hyperref}
\usetikzlibrary{positioning}

\emnlpfinalcopy

@@

%\begin{figure*}[t]
%\begin{tikzpicture}
%\node(tree) [] {\includegraphics[width=1\textwidth]{tree_653_de1_de2.pdf}};
%\node [below right = -2cm and  -8cm of tree]{\includegraphics[width=0.4\textwidth]{DAline-extract.png}};
%\end{tikzpicture}
%\begin{tabular}{c}
%\includegraphics[width=1\textwidth]{tree_653_ver2.png}\\
%\includegraphics[width=0.6\textwidth]{DAline-extract.png}
%\end{tabular}
%\caption{An example of a doubly annotated HUME en-de sentence. The color of the nodes correspond to their
%  HUME label: yellow (A), blue (B), and atomic nodes with their traffic light color. Nodes in which the annotators
%  disagree are split in color. The scale at the bottom right shows a sample of 10 raw DA assessments
%  for this example. }
%\label{fig:humeeg}
%\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

%While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
%differences and commonalities, it is important to note that the two measures are fundamentally different.
%Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
%accompanied by 10 raw DA scores assigned to that sentence.
%The figure illustrates the conceptual difference between the measures:
HUME and DA are conceputally very different metrics:
while DA standardises and averages scores across annotators to denoise the
crowd-sourced raw data, thus obtaining a single aggregate score,
HUME decomposes over a combinatorial structure, thus allowing to
localize the translation errors. We now turn to comparing HUME to a more
conceptually-related  measure, namely HMEANT.
